Appendix 2: Manuscript and Exploratory Code

### 2025-06-10 manuscript_code.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(worcs)
library(tidyverse)
library(gtsummary)
library(likert)
library(here)
library(corrplot)
library(ggstats)
library(lavaan)
library(lavaanPlot)
library(kableExtra)
library(naniar)
library(gridExtra)
#library(semPlot) # update plots to semPlot later
#library(blavaan) # could not get it to work with this model and synthetic data, try as sensitivity analysis later
#library(tidySEM) # https://github.com/yrosseel/lavaan/issues/359 lavaan does not work if tidySEM is loaded!
#library(griExtra) #used for combining multiple plots

# renv::status() to check 
# renv::snapshot() to add used and install to renv

@@

```{r}
eval=FALSE
gg_miss_var(
  data.fit2
  )
```

@@

```{r}
eval=FALSE
gg_miss_upset(data.fit2,nsets = 10,nintersects=40)
```

@@

```{r}
eval=FALSE
gg_miss_case_cumsum(
  data.fit2 %>% arrange(dttma)
)

@@

```{r}
eval=FALSE
gg_miss_fct(
  x = data.fit %>% select(-dttma,
                          -de01,
                          -de02,
                          -bd02,
                          -bd04,
                          -ss_psycown,
                          -ss_selfid,
                          -ss_donation,
                          ), 
  fct = ss_intention)

@@

```{r}
eval=FALSE
data.fit3 <- data.fit2 %>%
  select(-ss_psycown,
         -ss_selfid, 
         -ss_intention,
         -ss_donation)

@@

```{r}
#making bd02 the only variable in donation history

@@

```{r}
eval=FALSE
#https://stats.stackexchange.com/questions/340857/serial-mediation-in-r-how-to-setup-the-model

@@

```
```{r}
#Bivariate correlation table for paper

@@

```{r}
eval=FALSE
#if (fitmodels) {
  #fit.po02ss <- sem(po02ss.model,  
                    #estimator = "MLR", 
                    #missing = "listwise",
                    #data = data.fit2,
                    #auto.fix.first = FALSE, 
                    #std.lv = TRUE,
                    #fixed.x = TRUE

@@

```{r}
eval=FALSE
#lavaan::inspect(fit.po02ss,"r2")
```

```{r}
eval=FALSE
#fit.po02ss.est  <-standardizedSolution(fit.po02ss)
#fit.po02ss.est %>% select(-label,se,z) %>%  filter(op == '~')
```

@@

```{r}
labelsforplottingnull <- c(
  "ss_psycown" = "Psychological ownership",
  "ss_selfid"  = "Self-identity",
  "ss_intention" = "Intention",
  "ss_donation" = "Blood donation history"
)

@@

nBoots <- 1000

@@

```{r}
eval=FALSE
#fit.po04ss.est  <-standardizedSolution(fit.po04ss)
#fit.po04ss.est %>% select(-label,se,z) %>%  filter(op == '~')
```

@@

```{r}
eval=FALSE
#fit.po05ss.est  <-standardizedSolution(fit.po05ss)
#fit.po05ss.est %>% select(-label,se,z) %>%  filter(op == '~')
```

@@

```{r}
eval=FALSE
#lavaanPlot(
  #model = fit.po05ss, 
   #labels = labelsforplottingnull,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem05.pdf"))

@@

po02.model <- ' 
#measurement model
psycown =~ po01 + po02 + po03
selfid =~ si01 + si02 + si03
intention =~ it01 + it02 + it03
blooddonor =~ bd02 
#bd01 is just used for exclusion of "no"

@@

```{r}
eval=FALSE
#lavaan::inspect(fit.po02,"r2")
```

```{r}
eval=FALSE
#fit.po02.est  <-standardizedSolution(fit.po02)
#fit.po02.est %>% select(-label,se,z) %>%  filter(op == '~')
```

@@

#lavaanPlot(
  #model = fit.po02, 
   #labels = labelsforplotting,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/pllvsem02.pdf"))
```

@@

```{r}
#fit.po03.best <- parameterEstimates(fit.po03)
#fit.po03.best %>% select(-se,-z) %>% filter(op == "~")
```

@@

#factor_scores <- lavPredict(fit.po04, type = "lv") #taking factor scores from CFA 
factor_scores <- lavPredict(fit.po01.cfa, type = "lv")
head(factor_scores)
summary(factor_scores)

@@

#end of exploratory analysis
#knitr::knit_exit()

@@

```{r}
#fit.po05.est  <-standardizedSolution(fit.po05)
#fit.po05.est %>% select(-label,se,z) %>%  filter(op == '~')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(worcs)
library(tidyverse)
library(gtsummary)
library(likert)
library(here)
library(corrplot)
library(ggstats)
library(lavaan)
library(lavaanPlot)
library(kableExtra)
library(naniar)

library(gridExtra)
#library(semPlot) # update plots to semPlot later
#library(blavaan) # could not get it to work with this model and synthetic data, try as sensitivity analysis later
#library(tidySEM) # https://github.com/yrosseel/lavaan/issues/359 lavaan does not work if tidySEM is loaded!
# renv::status() to check 
# renv::snapshot() to add used and install to renv

@@

```{r}
eval=FALSE

gg_miss_var(
  data.fit2
  )
```

@@

eval=FALSE

gg_miss_upset(data.fit2,nsets = 10,nintersects=40)
```

@@

eval=FALSE

gg_miss_case_cumsum(
  data.fit2 %>% arrange(dttma)
)

@@

eval=FALSE

gg_miss_fct(
  x = data.fit %>% select(-dttma,
                          -de01,
                          -de02,
                          -bd02,
                          -bd04,
                          -ss_psycown,
                          -ss_selfid,
                          -ss_donation,
                          ), 
  fct = ss_intention)

@@

eval=FALSE

data.fit3 <- data.fit2 %>%
  select(-ss_psycown,
         -ss_selfid, 
         -ss_intention,
         -ss_donation)

@@

@@

eval=FALSE

#https://stats.stackexchange.com/questions/340857/serial-mediation-in-r-how-to-setup-the-model

@@

```{r}
#Bivariate correlation table for paper

@@

eval=FALSE
#if (fitmodels) {
  #fit.po02ss <- sem(po02ss.model,  
                    #estimator = "MLR", 
                    #missing = "listwise",
                    #data = data.fit2,
                    #auto.fix.first = FALSE, 
                    #std.lv = TRUE,
                    #fixed.x = TRUE

@@

eval=FALSE
#lavaan::inspect(fit.po02ss,"r2")

```{r}
eval=FALSE
#fit.po02ss.est  <-standardizedSolution(fit.po02ss)
#fit.po02ss.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

labelsforplottingnull <- c(
  "ss_psycown" = "Psychological ownership",
  "ss_selfid"  = "Self-identity",
  "ss_intention" = "Intention",
  "ss_donation" = "Blood donation history"
)

@@

```{r}
nBoots <- 1000

@@

```{r}
eval=FALSE
#fit.po04ss.est  <-standardizedSolution(fit.po04ss)
#fit.po04ss.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

```{r}
eval=FALSE
#fit.po05ss.est  <-standardizedSolution(fit.po05ss)
#fit.po05ss.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

eval=FALSE
#lavaanPlot(
  #model = fit.po05ss, 
   #labels = labelsforplottingnull,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem05.pdf"))

@@

po02.model <- ' 
#measurement model
psycown =~ po01 + po02 + po03
selfid =~ si01 + si02 + si03
intention =~ it01 + it02 + it03
blooddonor =~ bd02

#bd01 is just used for exclusion of "no"

@@

```{r}
eval=FALSE
#lavaan::inspect(fit.po02,"r2")

```{r}
eval=FALSE
#fit.po02.est  <-standardizedSolution(fit.po02)
#fit.po02.est %>% select(-label,se,z) %>%  filter(op == '~')

@@

#lavaanPlot(
  #model = fit.po02, 
   #labels = labelsforplotting,
  #node_options = list(shape = "box", fontname = "Helvetica"), 
  #edge_options = list(color = "grey"), 
  #coefs = TRUE, 
  #stand = TRUE,
  #sig=0.001
  #) %>% lavaanPlot::embed_plot_pdf(here("figures/pllvsem02.pdf"))

@@

```{r}
#fit.po03.best <- parameterEstimates(fit.po03)
#fit.po03.best %>% select(-se,-z) %>% filter(op == "~")

@@

#factor_scores <- lavPredict(fit.po04, type = "lv") #taking factor scores from CFA 
factor_scores <- lavPredict(fit.po01.cfa, type = "lv")

dim(factor_scores)
dim(data.fit2)

factor_scores <- lavPredict(fit.po04, type = "lv")
head(factor_scores)
summary(factor_scores)

@@

#end of exploratory analysis
#knitr::knit_exit()
=======
  de02 = data.fit2$de02,
  de01 = data.fit2$de01
)

ggplot(df_scores, aes(x = psycown, y = intention,
                      color = as.factor(de01))) +
  geom_point(alpha = 0.7, size = 2.5) +
  labs(title = "Latent Factor Scores by de01 and de02",
       x = "Psychological Ownership",
       y = "Donation Intention",
       color = "gender") +
  theme_minimal()

ggplot(df_scores, aes(x = p, y = intention,
                      color = as.factor(de01))) +
  geom_point(alpha = 0.7, size = 2.5) +
  labs(title = "Latent Factor Scores by de01 and de02",
       x = "Psychological Ownership",
       y = "Donation Intention",
       color = "gender") +
  theme_minimal()

ggplot(df_scores, aes(x = psycown, y = intention,
                      color = as.factor(de02),
                      shape = as.factor(de01))) +
  geom_point(alpha = 0.7, size = 2.5) +
  labs(title = "Latent Factor Scores by de01 and de02",
       x = "Psychological Ownership",
       y = "Donation Intention",
       color = "age",
       shape = "gender") +
  theme_minimal()

>>>>>>> ee3050c55c3e75c3dd19c1a8d96fa7c2f0d5d570

@@

```{r}
#fit.po05.est  <-standardizedSolution(fit.po05)
#fit.po05.est %>% select(-label,se,z) %>%  filter(op == '~')
